High-Dimensional Regularized Discriminant Analysis

### 2016-01-30 reports/paper-hdrda.Rnw
Thanked Mrs. Young.
Added coauthor organizations. #25

\usepackage{graphicx, amsmath, amssymb, bm, mathtools, amsthm, natbib, setspace, algorithm2e}

@@

\author{John A. Ramey, Caleb K. Stein, Phil D. Young, and Dean M. Young}

@@

>>>>

\usepackage{graphicx, amsmath, amssymb, bm, mathtools, amsthm, natbib, setspace, algorithm2e, authblk}

@@

%\author{John A. Ramey, Caleb K. Stein, Phil D. Young, and Dean M. Young}

\author[a]{John A. Ramey}
\author[b]{Caleb K. Stein}
\author[c]{Phil D. Young}
\author[d]{Dean M. Young}
\affil[a]{uStudio, Inc.}
\affil[b]{Myeloma Institute, University of Arkansas for Medical Sciences}
\affil[c]{Department of Management and Information Systems, Baylor University}
\affil[d]{Department of Statistical Science, Baylor University}

\renewcommand\Authands{ and }

@@

We thank Mrs. Joy Young for her numerous recommendations that enhanced the
quality of our writing.
